### 2022-06-14 tex/supplement.tex
Add more details on Jacobian correction

where $\boldsymbol{x}_n$ is the $n$-vector of ones.
The Jacobian has a shape $(n+1,n)$.
We can compute the density correction due to $\phi^{-1}$ as $\sqrt{|J^\top J}$:

>>>>

where $\boldsymbol{x}_n$ is the $n$-vector of ones.
The Jacobian has a shape $(n+1,n)$.
Even though $\phi$ is bijective, the output of $\phi$ is represented with an extra coordinate, so that $J$ is non-square.
It is possible to construct $\phi$ as the composition of a bijective function and a semi-orthogonal transformation that lifts the output from an $n$-dimensional vector to an $(n+1)$-dimensional vector.

The Jacobian would then factorize as $J = Q H$, where $Q$ is a size $(n+1,n)$ semi-orthogonal matrix so that $Q^\top Q = I_n$.
Orthogonal transformations leave the volume unchanged, so the density correction depends only on the unknown $H$.
Then $\sqrt{|J^\top J|} = \sqrt{|H^\top Q^\top Q H|} = \sqrt{|H^\top H|} = |H|$ computes the density correction.
